\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Include topology.pdf.
use clamped success time graph.
add captions to redesigned bridge and proxy screens.

\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth]{topology.png}
{\color {red} TODO}
\caption{
The chain of components involved in connecting to a website over Tor.
Most users do not need a proxy;
similarly only those users who face a censor need a bridge.
In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
We have shown the bridge as separate component
because of the special role it plays.
When a bridge is used, it takes the place of the first Tor hop.
}
\label{fig:topology}
\end{figure}

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=.85\textwidth]{old-flow.pdf}
\hrule
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
\caption{
Comparison of user flow in the ``OLD'' and ``NEW'' interfaces.
We collapsed the two bridge screens into one;
similarly the two proxy screens.
We swapped the order of the bridge and proxy configuration
so it matches the order of network components (Section~\ref{sec:components}).
We added a summary screen as a last step before initiating a connection.\\
\textbf{F}: first screen;
\textbf{B/B1/B2}: bridge screens;
\textbf{P/P1/P2}: proxy screens;
\textbf{S}: summary screen;
\textbf{Pr}: progress bar.
}
\label{fig:flow}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
		\caption{bridge screens} 
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
		\caption{proxy-screens} 
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics{time_to_success}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times;
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right
show the number of participants who did not finish
in the time alloted.
}
\label{fig:time_to_success}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics{time_to_success_clamped}
%\caption{
%Time to first success, by censorship environment and interface.
%Here, non-finishing participants are assigned a time of 40 minutes.
%}
%\label{fig:time_to_success_clamped}
%\end{figure}

@@

\section{Discussion} 
{\color {red} TODO: improvements.} \\
{\color {red} TODO: subjective observations.} \\
{\color {red} TODO: remaining issues.} \\
{\color {red} recommendations are below.} \\

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{topology}
\caption{
The chain of components involved in connecting to a website over Tor.
Most users do not need a proxy;
similarly only those users who face a censor need a bridge.
In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
We have shown the bridge as separate component
because of the special role it plays.
When a bridge is used, it takes the place of the first Tor hop.
}
\label{fig:topology}
\end{figure}

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=.85\textwidth]{old-flow.pdf}
\hrule
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
\caption{
Comparison of user flow in the ``OLD'' and ``NEW'' interfaces.
We collapsed the two bridge screens into one 
and also collapsed the two proxy screens into one.
We swapped the order of the bridge and proxy configuration
so it matches the order of network components (Section~\ref{sec:components}).
We added a summary screen as a last step before initiating a connection.\\
\textbf{F}: first screen;
\textbf{B/B1/B2}: bridge screens;
\textbf{P/P1/P2}: proxy screens;
\textbf{S}: summary screen;
\textbf{Pr}: progress bar.
}
\label{fig:flow}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
		\caption{In the ``OLD'' interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
		be configured and directs to the bridge configuration screen (B2). 
		The ``NEW'' interface gives users advice on configuring bridges
		while giving the option of not configuring a bridge, on one screen (B).} 
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
		proxy configuration screen (P2). The ``NEW'' interface checks the local machine for if a proxy configured,
		and informs the user if the proxy is required, and if so, what those settings are (P).'' }
\end{figure*}

@@

%\begin{figure}
%\centering
%\includegraphics{time_to_success}
%\caption{
%Time to first success, by censorship environment and interface.
%The dots show the raw completion times;
%while the boxplots show the medians and interquartile ranges.
%The ``DNF'' figures at the right
%show the number of participants who did not finish
%in the time alloted.
%}
%\label{fig:time_to_success}
%\end{figure}

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right show the number of participants 
who did not finish in the time alloted.
Here, non-finishing participants are assigned a time of 40 minutes.
}
\label{fig:time_to_success_clamped}
\end{figure}

@@

\section{Discussion} 
{\color {red} TODO: remaining issues.} \\
{\color {red} recommendations are below.} \\
